### 2017-12-14 Documents/bootcamp_project_turnin.tex
fixed typo
more typos fixed

Below are the step by step details and format that I ask of you to post your project in. Not following these instructions exactly will result in a 10 percent reduction in your project score.

@@

All of this must be done prior to midnight, at the end of the day December 21st. Finally, \textbf{do not modify} your work after the 21st until you have recited a grade from me. After you have received a grade, you may treat the project as yours as continue to work on it as you like.

>>>>

Below are the step by step details and format that I ask of you to post your project in. Not following these instructions exactly will result in a 10 percent reduction in the available points that your project can receive.

@@

All of this must be done prior to midnight, at the end of the day December 21st. Finally, \textbf{do not modify} your work after the 21st until you have received grade from me. After you have received a grade, you may treat the project as yours as continue to work on it as you like.
